Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-12 sas2015/content/related.tex
tweaks to save space

\section{Related Work}
  \label{sec:Related}
%\otodo{Should we remove first initials in this section?}
The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.
\commentout{
Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
}
IFDS has been used to encode a variety of data-flow problems such as typestate analysis%
\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
\commentout{(detecting errors and validating properties of programs at compile time)}%
~\cite{DBLP:conf/birthday/KreikerRRSWY13}. IFDS has been broadly used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.

@@

Several extensions of the IFDS algorithm have been proposed to improve its precision,
efficiency, and expressiveness. Naeem and Lhot\'ak~\cite{naeem2010pei} propose
four extensions: two to improve efficiency on certain kinds of IFDS problems,
one to improve expressiveness to a wider range of IFDS problems, and one
to improve precision when applying the IFDS algorithm to programs in SSA form.
All of these extensions are orthogonal to and could be combined with the approach
that we present in this paper. In contrast to these techniques, our approach targets
analysis precision, not efficiency or expressiveness.

@@

Two other extensions target efficiency. Bodden et~al.~\cite{bodden2013spl} presents a framework
for applying IFDS analyses to software product lines. Their approach enables the analysis of
all possible products derived from a product line in a single analysis pass. Like our approach,
their approach transforms IFDS problems to IDE problems. The micro-functions keep track
of the possible program variations specified by the product line.
Rodriguez and Lhot\'ak evaluate a parallelized implementation of the IFDS algorithm using actors~\cite{rodriguez2010concurrent} that can take advantage of multiple processors.
%However, neither of those works is concerned with improving the precision of IFDS results.

@@

The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs was introduced by Tip~\cite{DBLP:journals/scp/Tip15}. The possibility of using IDE to achieve this is mentioned, but not elaborated upon. Our work presents a concrete solution to the problem and an implementation of that solution.

Sridharan et~al.'s improvements to the precision of pointer analysis
for Ja\-va\-Script programs~\cite{DBLP:conf/ecoop/SridharanDCST12} also
eliminate infeasible paths. Instead of infeasible paths
between dynamically dispatched method calls, their approach eliminates
infeasible paths between reads and writes of different properties
%(the JavaScript analogue of fields) 
of an object. 
%Unlike in more static languages,
%property names in JavaScript are first class values (strings). When a loop indexed by
%property names updates the properties of objects, the loop body is extracted into a function
%and analyzed context sensitively with a separate context for each property name.
The approach differs from ours in that it targets points-to analysis rather
than IFDS analyses, in that it targets infeasible paths due to different
property names rather than different dynamically dispatched methods,
and in that it employs context sensitivity to improve precision.

@@

Our approach superficially resembles, but is orthogonal, to context
sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), while we analyze control flow paths instead.
Also, object-sensitive points-to analysis is flow-insensitive, while
the IFDS and IDE algorithms are flow-sensitive, and our transformation only makes sense
in a flow-sensitive setting (since a flow-insensitive analysis already
introduces many more infeasible control flow paths).

>>>>

\section{Related Work}
  \label{sec:Related}
%\otodo{Should we remove first initials in this section?}
The IFDS algorithm is an instance of the functional approach to data-flow analysis developed by Sharir and Pnueli~\cite{pnueli1981two}.
\commentout{
Their algorithm is based on computing \textit{summary functions} that return the data-flow value at the end of a procedure, given the data-flow value at the start of the procedure. IFDS problems form a more restricted set of data-flow problems: unlike in the functional approach, IFDS flow functions have to be distributive, and the set of data-flow facts $D$ has to be finite. However, the IFDS algorithm is more general than Sharir's and Pnueli's algorithm in that it can handle programs containing local variables and parameters in recursive methods.
}
IFDS has been used to encode a variety of data-flow problems such as typestate analysis%
\commentout{(determining which operations can be performed on an object at a given program point)}~\cite{naeem2008typestate,DBLP:conf/pldi/ZhangMGNY14} and shape analysis%
\commentout{(detecting errors and validating properties of programs at compile time)}%
~\cite{DBLP:conf/birthday/KreikerRRSWY13}. IFDS has been used~\cite{DBLP:conf/pldi/ArztRFBBKTOM14,tripp2009taj} and extended~\cite{DBLP:conf/sigsoft/LerchHBM14} to solve taint-analysis problems.

@@

Naeem and Lhot\'ak~\cite{naeem2010pei} proposed several extensions of IFDS.
In particular, they propose several techniques for improving the algorithm's 
efficiency, as well as a technique that improves expressiveness by extending
applicability to a wider class of dataflow analysis problems. 
These extensions are orthogonal to, and could be combined with the approach
presented in this paper. Our work differs from theirs by targeting
analysis precision, not efficiency or expressiveness.

@@

Bodden et~al.~\cite{bodden2013spl} presents a framework
for applying IFDS analyses to software product lines. Their approach enables the analysis of
all possible products derived from a product line in a single analysis pass. Like our approach,
their approach transforms IFDS problems to IDE problems. The micro-functions keep track
of the possible program variations specified by the product line.
Rodriguez and Lhot\'ak evaluate a parallelized implementation of the IFDS algorithm using actors~\cite{rodriguez2010concurrent} that can take advantage of multiple processors.
%However, neither of those works is concerned with improving the precision of IFDS results.

@@

The idea of using correlated calls to remove infeasible paths in data-flow analyses of object-oriented programs 
was introduced by Tip~\cite{DBLP:journals/scp/Tip15}. The possibility of using IDE to achieve this is mentioned, 
but not elaborated upon. Our work is the first to present and implement a concrete solution.

Recent work on correlation tracking for JavaScript~\cite{DBLP:conf/ecoop/SridharanDCST12} 
also eliminates infeasible paths. Instead of infeasible paths
between dynamically dispatched method calls, their approach eliminates
infeasible paths between reads and writes of different properties
of an object. 
%Unlike in more static languages,
%property names in JavaScript are first class values (strings). When a loop indexed by
%property names updates the properties of objects, the loop body is extracted into a function
%and analyzed context sensitively with a separate context for each property name.
The approach differs from ours in that it targets points-to analysis rather
than IFDS analyses, in that it targets infeasible paths due to different
property names rather than different dynamically dispatched methods,
and in that it employs context sensitivity to improve precision.

@@

Our approach superficially resembles, but is orthogonal, to context
sensitivity, including such variations as object sensitivity~\cite{DBLP:conf/issta/MilanovaRR02,DBLP:journals/tosem/MilanovaRR05}.
Context-sensitive
points-to analysis is orthogonal to our work because it analyzes the
flow of data (pointers), whereas we analyze control flow paths.
Also, object-sensitive points-to analysis is flow-insensitive, while
IFDS and IDE are flow-sensitive analyses. Note that our transformation only makes sense
in a flow-sensitive setting since a flow-insensitive analysis already
introduces many infeasible control flow paths.
